---
title: "bridgedist R package"
author: "Bruce Swihart"
date: "April 18, 2016"
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/swihart/bridgedist.svg?branch=master)](https://travis-ci.org/swihart/bridgedist)

Package: bridgedist

Title: An Implementation of the Bridge Distribution with Logit-Link as in Wang and Louis (2003)

Description: An implementation of the bridge distribution with logit-link in R.
    In Wang and Louis (2003), such a bridge distribution was derived as the distribution of
    the random intercept that facilitated having a conditional logistic regression that when
    marginalized by integrating out the random intercept left a marginal logistic regression,
    and the conditional and marginal regression coefficients are a scalar multiple of each other.

```{r, eval=FALSE}
library(devtools)
install_github(repo = "bridgedist", username = "swihart")
library(bridgedist)
```

```{r, include=FALSE}
library(bridgedist)
```

```{r}
dbridge(0)
pbridge(0)
qbridge(0.5)
mean(rbridge(100))
```
